\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{// All comments are NOT created equal}

### 2015-05-17 paper/paper.tex
preliminaries

\subsection{ROS}

\subsection{Octomap}
\ednote{DENIS}

\subsection{Robot Overview}
\ednote{can move and has a pan tilt unit and a sensor}

@@

>>>>

\subsection{ROS \& Octomap}
For this research project we will make use of the Robot Operating System (ROS). ROS is a framework for creating robot software.  Within ROS, this project will use the octomap_server \cite{hornung13auro}.\\

The octomap_server works by loading a 3D map and distributing it to nodes in a compact binary format. Thus it can build and save 3D OctoMaps.\\

\subsection{Robot Overview}

The robot we will be using in this project has the following basic capabilities:
\begin{itemize}
\item movement along the x, y, and z axes,
\item mapping functionality through sensors. 
\end{itemize}

Using these basic capabilities we are able to map sample reefs.

@@

\ednote{add octomap image}
